Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy

### 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Update R1-Renyi-entropy-sar.qmd

print(table_combined_result)
```
\textcolor{blue}{
We applied the proposed test to SAR images using sliding windows of $7 \times 7$ pixels. 
For each window, we computed the test statistic and calculated the $p$-value that quantifies the statistical evidence against local homogeneity. 
High $p$-values, e.g., $p > 0.05$, indicate no evidence to reject homogeneity, while low values ($p < 0.05$) suggest statistically significant deviations and are interpreted as heterogeneity.
}
<!-- Note that the visual outputs in Figs.~\ref{fig:london}--\ref{fig:dublin} show the $p$-values obtained from the hypothesis testing procedure, not the test statistic or entropy values. -->

@@

kable(SAR_data, 
      format = "latex",
      booktabs = TRUE,
      align = "ccccccc",
      escape = FALSE,
      digits = 2,
      label = "table_param",
      centering = TRUE,
      caption = "Parameters of selected SAR images.",
      table.envir = "table", position = "H") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 22) %>% 
  kable_styling(full_width = TRUE) %>%
  column_spec(1, width = "3.0cm") %>%
  column_spec(2, width = "4.5cm") %>%
  column_spec(3, width = "1.5cm") %>%
  column_spec(4, width = "4cm") %>%
  column_spec(5, width = "1.5cm") %>%
  column_spec(6, width = "4.0cm") %>%
  column_spec(7, width = "4.5cm")

>>>>

print(table_combined_result)
```
\textcolor{blue}{
We applied the proposed test to SAR images using sliding windows of $7 \times 7$ pixels. 
For each window, we computed the test statistic and calculated the $p$-value that quantifies the statistical evidence against local homogeneity. 
High $p$-values, e.g., $p > 0.05$, indicate no evidence to reject homogeneity, while low values, e.g., $p < 0.05$, suggest statistically significant deviations and are interpreted as heterogeneity.
}
<!-- Note that the visual outputs in Figs.~\ref{fig:london}--\ref{fig:dublin} show the $p$-values obtained from the hypothesis testing procedure, not the test statistic or entropy values. -->

@@

kable(SAR_data, 
      format = "latex",
      booktabs = TRUE,
      align = "ccccccc",
      escape = FALSE,
      digits = 2,
      label = "table_param",
      centering = TRUE,
      caption = "Parameters of selected SAR images",
      table.envir = "table", position = "H") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 22) %>% 
  kable_styling(full_width = TRUE) %>%
  column_spec(1, width = "3.0cm") %>%
  column_spec(2, width = "4.5cm") %>%
  column_spec(3, width = "1.5cm") %>%
  column_spec(4, width = "4cm") %>%
  column_spec(5, width = "1.5cm") %>%
  column_spec(6, width = "4.0cm") %>%
  column_spec(7, width = "4.5cm")
